%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Amazon} % Organization
    {Software Development Engineer} % Job title
    {Seattle, WA} % Location
    {Dec. 2018 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained IMDb's image and content acquisition
        systems and full-stack features, afterwards the core API}
        \item {Migrated these systems from legacy Perl \& monolith Java to
        service-oriented Java \& serverless AWS (Node.js, GraphQL), respectively}
        \item {Built internal web applications including image management
        tooling (Spring \& React) and core API explorer (Express \& React)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {NASA Ames Research Center} % Organization
    {Clinic Team Researcher} % Job title
    {Claremont, CA} % Location
    {Aug. 2017 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team of five to improve upon scheduling
        and execution in multi-robot systems with limited communication}
        \item {Designed, implemented, and tested three algorithms that reduce
        rescheduling when compared to existing algorithms from literature}
        \item {Submitted and presented a paper at IntEx ICAPS 2018:
        \url{https://www.cs.hmc.edu/HEAT/papers/Chu_et_al_INTEX_2018.pdf}}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Harvey Mudd College} % Organization
    {Tutor and Grader} % Job title
    {Claremont, CA} % Location
    {Sep. 2015 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored students and graded assignments for
        ``Probability II'' (1 semester),
        ``Programming Languages'' (1 semester),
        ``Computer Systems'' (1 semester),
        ``Data Structures \& Program Development'' (2 semesters),
        and ``Introduction to Computer Science'' (1 semester)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pure Storage} % Organization
    {Software Engineer Intern} % Job title
    {Bellevue, WA} % Location
    {May 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Map View, a spatial data visualization tool on Pure1's
        dashboard, using TypeScript, Angular, D3, \& Google Maps API}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ubiqua} % Organization
    {Software Engineer Intern} % Job title
    {Panama City, Panama} % Location
    {Jun. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built Ubiqua POC, a Ruby on Rails service that processes
        supermarket purchase orders, and integrated with the first client}
        \item {Identified product code inconsistencies in product distributors’
        databases using Active Record}
        \item {Prototyped a Rails, Backbone, \& CoffeeScript application for
        distributor warehousemen and invoicers to process refunds}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Harvey Mudd College} % Organization
    {Student Researcher} % Job title
    {Claremont, CA} % Location
    {Jun. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team of four to create Loqus, a Python Flask
        application that allows users to share files conveniently with people
        nearby}
        \item {Designed the UI, implemented the front-end using Bootstrap, and
        integrated Google Maps API}
        \item {Pitched at two HMCEN conferences, gave a CS Department
        talk, and delivered a guest speech for HMC's entrepreneurship class}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
